---
title: "Influence Measures in Linear Models"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Influence Measures in Linear Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides an overview of the `DATA501A2DM` package, which is used to calculate one of the three influence measure values and plot them.        

* Cook's Distance (Cook, 1977)
* DFFITS (Belsley, 1980)
* Hadis Influence Measure (hadi, 1992)        

The calculate methods are from the book "Regression Analysis by Example (Hadi, Ali S; 2012; 5th Edition,Chapter 4)"       

# Installation

You can install the package using the following commands:

```{r}
# Conditional installation code
if (!requireNamespace("DATA501A2DM", quietly = TRUE)) {
  devtools::install_github("nihaohelloworld/DATA501A2_DistanceMeasure")
}
```


# Example Usage

We will use the built-in `mtcars` dataset to demonstrate how to apply the `plot_influence_measure` function.        

## Fit a Linear Model       

First, we need to fit a linear model using the `lm` function:       

```{r}
lm_model <- lm(mpg ~ wt + hp, data = mtcars)
summary(lm_model)
```

## Plot Cook's Distance       

Next, we will calculate Cook's Distance, DFFITS, Hadi's Influence Measure separately and plot it:       

```{r}
library(DATA501A2DM)
# Plot Cook's Distance
plot_influence_measure(mtcars, lm_model, method = "cooks")

# Plot DFFITS
plot_influence_measure(mtcars, lm_model, method = "dffits")

# Plot Hadi's Influence Measure
plot_influence_measure(mtcars, lm_model, method = "hadi")
```

# Conclusion        

The `plot_influence_measure` function is a versatile tool for assessing the influence of individual data points in linear models. By calculating and visualising different influence measures, you can better understand the robustness of your model.        

# references        

* Regression Analysis by Example (Hadi, Ali S; 2012; 5th Edition)       
* Cooks Distance Measure (Cook, 1977)       
* DFFITS (Welsch and Kuh, 1977; Belsley, 1980)        
* Hadis Influence Measure (Hadi, 1992)        





















