---
title: "Influence_Measure_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Influence_Measure_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides an overview of the `DATA501A2DM` package, which is used to calculate one of the three influence measure values and plot them.        

* Cook's Distance (Cook, 1977)
* DFFITS (Belsley, 1980)
* Hadis Influence Measure (hadi, 1992)        

The calculate methods are from the book "Regression Analysis by Example (Hadi, Ali S; 2012; 5th Edition,Chapter 4)"       

# Installation

You can install the package using the following commands:


# Usage

```{r}
library(DATA501A2DM)

# Fit a linear model
lm_model <- lm(mpg ~ wt + hp, data = mtcars)

# Plot Cook's Distance
plot_influence_measure(mtcars, lm_model, method = "cooks")

# Plot DFFITS
plot_influence_measure(mtcars, lm_model, method = "dffits")

# Plot Hadi's Influence Measure
plot_influence_measure(mtcars, lm_model, method = "hadi")
```

